---
title: "P8105_hw3_qh2251"
author: "Paulina Han"
date: "2021/10/14"
output: github_document
---
```{r}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

# Problem 1

```{r}
#load the data
data("instacart")

# summary the aisles
 aisels_df1 = 
   instacart %>% 
  group_by(aisle) %>% 
  summarize(num = n()) %>% 
   arrange(desc(num))

# plotting the aisles and their sales
 aisels_df2 =   
  instacart %>% 
  group_by(aisle) %>% 
  summarize(num = n()) %>% 
    filter(num > 10000) %>% 
    arrange(desc(num))
    
 aisels_df2 %>% 
   mutate(
     aisle = factor(aisle),
     aisle = fct_reorder(aisle, num)
   ) %>% 
 ggplot(aes(x = aisle, y = num)) + 
  geom_point() + 
  labs(
    title = "Aisle Sale",
    x = "aisles",
    y = "number of item",
    ) +
   theme(axis.text.x=element_text(angle = 90, vjust = 0.5, hjust = 1))
    
# most popular product in each aisle
 aisels_df3 = 
   instacart %>% 
   filter(aisle %in% c("baking ingredients","dog food care","packaged vegetables fruits")) %>% 
   group_by(aisle, product_name) %>% 
   summarise(product_num = n()) %>% 
   arrange(desc(product_num),.by_group = T) %>% 
   slice_max(order_by = product_num,n = 3)  

#make a table
   aisels_df3 %>% 
    knitr::kable()
 
# mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week
hour_df = 
  instacart %>% 
  filter(product_name %in% c("Pink Lady Apples","Coffee Ice Cream"))%>% 
  group_by(product_name,order_dow) %>% 
  summarize(mean_order_time = round(mean(order_hour_of_day),2)) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_order_time
  ) 

#rename the colunms
colnames(hour_df) = c("product_name","Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday")
 
#print table
hour_df %>% 
  knitr::kable()
  
```

There are 134 aisles and the _fresh vegetables aisle_ is the where most items are ordered from.

# Problem 2


```{r}

data("brfss_smart2010")
#clean variable names
brfss_smart2010_1=
 brfss_smart2010 %>% 
  rename(
    State = Locationabbr,
    Location = Locationdesc
  )

#subset a new data set brfss_df_1
brfss_df_1 = 
  brfss_smart2010_1 %>% 
  filter(Topic == "Overall Health") %>% 
  filter(Response %in% c("Excellent","Very good","Good","Fair","Poor")) %>% 
  mutate(Response = as.factor(Response)) %>% 
  mutate(Response = factor(Response, levels = c("Poor", "Fair", "Good","Very good","Excellent")))

#In 2002, which states were observed at 7 or more locations? What about in 2010?
#2002
#group by doesn't work
 brfss_df_2 = 
   brfss_df_1 %>% 
   filter(Year == 2002) %>% 
   group_by(State) %>%
  summarize(loc_num = n())

brfss_df_2 = 
  brfss_df_1 %>% 
  filter(Year == 2002) %>% 
  group_by(State) %>%
  summarize(loc_num = n())%>% 
  filter(loc_num >= 7)

#2010
brfss_df_3 = 
  brfss_df_1 %>% 
  filter(Year == 2010) %>% 
  group_by(State) %>%
  summarize(loc_num = n())%>% 
  filter(loc_num >= 7)
#states in 2002
states_2002 = pull(brfss_df_2,State)

states_2010 = pull(brfss_df_3,State)

#answer only Excellent
brfss_df_4 = 
  brfss_df_1 %>% 
  filter(Response == "Excellent") %>% 
  group_by(Year,State) %>% 
mutate(
  mean_value = mean(Data_value,na.rm = T)) %>% 
  select(Year, State, mean_value) %>% 
  distinct() %>% 
  arrange(Year)
 
#plot
brfss_df_4 %>% 
  ggplot(aes(x = Year, y = mean_value, color = State))+
  geom_line()+
  theme(legend.position = "right")

#Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State
 

brfss_df_5 =
  brfss_df_1 %>% 
  filter(Year %in% c(2006,2010)) %>% 
  filter(State == "NY")


brfss_df_5 %>% 
ggplot(aes(x = Location , y = Data_value))+
  geom_point()+
  facet_grid(.~ Year)+
   theme(axis.text.x=element_text(angle = 60, vjust = 0.5, hjust = 1))# response?

  
  
  

```

# Probelm 3

```{r}
ACC_df = read_csv("./homework3_files/accel_data.csv")

ACC_df1 =
  ACC_df %>% 
  janitor::clean_names() %>%
  rename(id = day_id) %>% 
  mutate(weekdays = ifelse(day %in% c("Monday","Tuesday","Wednesday","Thursday","Friday"),1,0)) #weekday=1,weekend=0

obs = nrow(ACC_df1)
col = ncol(ACC_df1)

```

**Description**

There are `r obs` observation in this data set which represent the days when the data were collected. There are `r col` variables which includes `week` variable indicating the number of week and `id` variable indicating the number of days. The `day` variable represent the week names of the day. Variable `activity_1` to `activity_1440` indicates the activity counts in every minute starting from midnight throughout the day. `weekdays` variable is a binary variable indicating if it is weekend or not by labeling weekdays as 1 and weekend as 0.

```{r}
# activity counts by day

ACC_df2 =
  ACC_df1 %>% 
  mutate(total = rowSums(select(ACC_df1,activity_1:activity_1440))) %>% 
  select(week,id,weekdays,day,total) 

#table
  knitr::kable(ACC_df2)

```
There aren't any apparent trend from this table.

```{r}

#plot #有问题

Activity = 
  ACC_df1 %>% 
  select(activity_1:activity_1440) %>% 
  t() %>% 
  as.data.frame()

time_of_the_day = as.vector(colnames(Activity))

new_df = bind_cols(time_of_the_day,Acticity)

day_of_the_week = ACC_df1 %>% 
  select(day)

colnames(new_df) = c("time", day_of_the_week)

 
new_df %>% 
ggplot(aes( x = time, color = day))+ 
  geom_line()+
  theme(legend.position = "right")


```


